The Response Time of Toronto's Paramedic Service: How effective is the city's emergency medical care?

### 2023-02-03 outputs/paper/paper.qmd
Update paper.qmd
* Added additional comments
* Fixed code styling

  # Make the table headers bold
  row_spec(0,bold=TRUE) |>

@@

  # Create new descriptor column 
  cbind(descriptor = c("Sudden Cardiac Arrest", "Resuscitative care", "Emergent care", "Urgent care", "Less urgent care", "Non-urgent care")) |>

  # Rename all columns to human-friendly format
  rename("Response Level" = "patient_category", "Response Time (Mins)" = "plan_in_minutes", "Level Descriptor" = "descriptor") |>

  # Render table
  knitr::kable(align = "l", booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(font_size = 10, latex_options = "hold_position", full_width = TRUE) |>
  row_spec(0,bold=TRUE)

>>>>

  # Make the table headers bold
  row_spec(0, bold = TRUE) |>

@@

  # Create new descriptor column 
  cbind(descriptor = c(
    "Sudden Cardiac Arrest", 
    "Resuscitative care", 
    "Emergent care", 
    "Urgent care", 
    "Less urgent care", 
    "Non-urgent care")
  ) |>

  # Rename all columns to human-friendly format
  rename(
    "Response Level" = "patient_category", 
    "Response Time (Mins)" = "plan_in_minutes", 
    "Level Descriptor" = "descriptor"
  ) |>

  # Render table
  knitr::kable(align = "l", booktabs = TRUE, escape = FALSE, linesep = "") |>

  # Make the table headers bold
  row_spec(0, bold = TRUE)
